An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-04-06 tex/paper.tex
Correct bib compilation for the Arxiv.
Correct affiliation for Geraint.
2nd modification:
- Adding references to multiprocess
- Typo found by Geraint

% Commenting out as this overrides the section titles.
%\pagestyle{fancy}
%\definecolor{mygray}{gray}{0.6}
%\renewcommand\headrule{}
%\rhead{\footnotesize 3}
%\rhead{\textcolor{gray}{UP JORS software Latex paper template version 0.1}}

% Nicer bibliography management
\usepackage[backend=biber, firstinits=true, url=true, isbn=true]{biblatex}
\addbibresource{references.bib}
%-----------------------------

@@

\begin{multicols}{2}
    \begin{enumerate}[noitemsep,topsep=0pt]
\item Development; Cardiff University
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; Cardiff University
\item Development; St. Nicholas Catholic High School, Hartford
\item Development; Cardiff University
\item Development; Cardiff University
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; The University of Edinburgh
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; The University of Manchester
\item Development; Cardiff University
\item Development; Not affiliated
\item Development; Not affiliated
    \end{enumerate}
\end{multicols}

@@

\begin{equation}
    \begin{pmatrix}
        R,R & S,T\\
        S,S & P,P
    \end{pmatrix}\quad\text{such that } T>R>P>S \text{ and } 2R > T + S
    \label{equ:one-shot}
\end{equation}

@@

\begin{itemize}[noitemsep,topsep=0pt]
    \item Noisy tournaments;
    \item Tournaments with probabilistic ending of interactions;
    \item Ecological analysis of tournaments;
    \item Morality metrics based on \cite{Singer-Clark2014};
    \item Transformation of strategies (in effect giving an infinite number of
        strategies);
    \item Classification of strategies according to multiple dimensions.
    \item Gathering of full interaction history for all interactions.
\end{itemize}

@@

\printbibliography
\end{document}

>>>>

% Commenting out as this overrides the section titles.
\pagestyle{fancy}
\definecolor{mygray}{gray}{0.6}
\renewcommand\headrule{}
\rhead{\footnotesize 3}
\rhead{\textcolor{gray}{UP JORS software Latex paper template version 0.1}}

% Nicer bibliography management
\usepackage[backend=bibtex, firstinits=true, url=true, isbn=true]{biblatex}
\addbibresource{references.bib}
%-----------------------------

@@

\begin{multicols}{2}
    \begin{enumerate}[noitemsep,topsep=0pt]
\item Development; Cardiff University
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; Cardiff University
\item Development; St. Nicholas Catholic High School, Hartford
\item Development; Cardiff University
\item Development; Cardiff University
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; The University of Edinburgh
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; Cardiff University
\item Development; The University of Manchester
\item Development; Cardiff University
\item Development; Not affiliated
\item Development; Not affiliated
    \end{enumerate}
\end{multicols}

@@

\begin{equation}
    \begin{pmatrix}
        R,R & S,T\\
        T,S & P,P
    \end{pmatrix}\quad\text{such that } T>R>P>S \text{ and } 2R > T + S
    \label{equ:one-shot}
\end{equation}

@@

\begin{itemize}[noitemsep,topsep=0pt]
    \item Noisy tournaments.
    \item Tournaments with probabilistic ending of interactions.
    \item Ecological analysis of tournaments.
    \item Morality metrics based on \cite{Singer-Clark2014}.
    \item Transformation of strategies (in effect giving an infinite number of
        strategies).
    \item Classification of strategies according to multiple dimensions.
    \item Gathering of full interaction history for all interactions.
    \item Parallelization of computations for tournaments with a high
        computational cost \cite{Pathos, Mckerns2011}.
\end{itemize}

@@

\printbibliography
%\bibliographystyle{plain}
%\bibliography{references.bib}
\end{document}
